---
title: "The Seven Wonders of the RMarkdown World" # comments in YAML
subtitle: "<br/>...and counting"
author: "Andrew Clark - @pssguy"
date: "2016/12/13"
output:
  xaringan::moon_reader:
    yolo: false # You Only Live Once shows up if true, not so random images of karl appear
    lib_dir: libs
    nature:
      #autoplay: 30000
      highlightStyle: github
      highlightLines: true # come out yellow - I think see below
--- 

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE) 
```

# Outputs

- Dashboard
- Journal
- Website
- Blog
- Presentation
- Book

<!-- Will want to subslide this? maybe with image for each -->

---

# Formats

- HTML
- pdf
- MS Word
- epub
- MOBI


---

# Image of all types of output

---

wordcloud of (Markdown,Pandoc,Sweave,knitr)

  R eally    
aM azing    
  A rsenal of    
  R endered    
  K nitted    
  D ocumentation    
  O utput    
  W ithout    
kN owhow

---

# Basic Document

 - YAML
 - Simple Text
 - code chunks


---

# In RStudio

---

# In viewer

---

# View HTML


---

# Similar concept irrespective of output

libraries
data

```{r eval=FALSE, tidy=FALSE}

# Data manipulation and static graphing
library(tidyverse)

# htmlWidgets
library(plotly) # interactive charts
library(DT)     # sophisticated tables
library(leaflet) # mapping

# data
library(Lahman)

masterInfo <- Master %>%
  select(playerID, birthYear, birthMonth, nameLast,
         nameFirst, bats)

batting <- battingStats() %>% 
  # left_join(salaries, 
  #           by =c("playerID", "yearID", "teamID")) %>%
  left_join(masterInfo, by = "playerID") %>%
  mutate(age = yearID - birthYear - 
           1L *(birthMonth >= 10)) %>%
  arrange(playerID, yearID, stint)

eligibleHitters <- batting %>%
  filter(yearID >= 1900 & PA > 450)

topHitters <- eligibleHitters %>%
  group_by(yearID) %>%
  filter(BA == max(BA)| BA >= .400) %>%
  mutate(ba400 = BA >= 0.400) %>%
  mutate(name=paste0(nameFirst," ",nameLast)) %>% 
  select(playerID, yearID, name, 
         BA, ba400)

sort(names(topHitters))

topHitters %>% 
  plot_ly(x=~yearID,y=~BA)

topHitters %>% 
  plot_ly(x=~yearID,y=~BA, color=~name, hoverinfo = "text",
text = ~ paste(name,
               "<br>Year: ",yearID,
               "<br>BA: ",BA)) %>%
  layout(hovermode = "closest",
        # height = 400,
       #  autosize = F,
         title="The Last to Hit .400?",
         xaxis=list(title="Season"),
         yaxis=list(title="Batting Average"
         )
  )  %>% 
  config(displayModeBar = F,showLink = F)


```




- Dashboard

