---
title: "The Seven Wonders of the RMarkdown World" # comments in YAML
subtitle: "<br/>...and counting"
author: "Andrew Clark - @pssguy"
date: "2016/12/13"
output:
  xaringan::moon_reader:
    yolo: false # You Only Live Once shows up if true, not so random images of karl appear
    lib_dir: libs
    nature:
      #autoplay: 30000
      highlightStyle: github
      highlightLines: true # come out yellow - I think see below
--- 

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE) 
```

# Outputs

- Dashboard
- Journal
- Website
- Blog
- Presentation
- Book

<!-- Will want to subslide this? maybe with image for each -->

---

# Formats

- HTML
- pdf
- MS Word
- epub
- MOBI


---

# Image of all types of output

---

wordcloud of (Markdown,Pandoc,Sweave,knitr)

  R eally    
aM azing    
  A rsenal of    
  R endered    
  K nitted    
  D ocumentation    
  O utput    
  W ithout    
kN owhow

---

# Basic Document

 - YAML
 - Simple Text
 - code chunks


---

# In RStudio

---

# In viewer

---

# View HTML


---

# Similar concept irrespective of output

libraries
data

```{r eval=FALSE, tidy=FALSE}

# Data manipulation
library(tidyverse)

# htmlWidgets
library(plotly)
library(DT)
library(leaflet)

# data
library(Lahman)


```




- Dashboard

